Automated discovery \\ of interpretable gravitational-wave population models

### 2022-07-11 src/tex/ms.tex
Add units to table
Correct selection strategy

\begin{table*}[hbt!]
    \begin{center}
    \begin{tabular}{ l l l l }
    \hline
    \hline
    Complexity &  Score & Loss & Expression\\
    \hline
    \hline
    16 & 0.126   & 0.212  & $3.72 \rm{Cond}{\left(M - 9.27,0.9^{M} \right)} + 3.72 \rm{Gauss}{\left(0.52 M - 4.85 \right)}$\\[0.4em]
    % Add more space between rows of table^
    25 & 0.501   & 0.0352 & $3.89 \left(\rm{Gauss}{\left(0.19 M - 6.54 \right)} + 0.45\right) \rm{Cond}{\left(M - 9.12,0.91^{M} \right)}$\\
    & & & $ + 3.89 \rm{Gauss}{\left(0.5 M - 4.8 \right)}$\\[0.4em]
    48 & 0.00771 & 0.0108 & $\left(\rm{Cond}{\left(M - 9.42,0.62 \cdot 0.9^{M} \right)} + 1.44 \rm{Gauss}{\left(0.51 M - 4.88 \right)}\right)$\\
    & & & $\left(5.11 \rm{Gauss}{\left(0.06 M - 4.67 \right)} + 7.82 \rm{Gauss}{\left(0.17 M - 5.86 \right)} + 3.26\right)$\\
    \hline
    \hline
    \end{tabular}
    \caption{Expressions obtained through symbolic regression with \pysr.
    In the search we perform, there are 30 equations with different complexities.
    We select three most representative equations by setting loss thresholds, and selecting the highest scoring expression below each threshold. This strategy rules out trivial expressions with low accuracy which had high scores only because they were adjacent to other trivial expressions.}
    \label{tab:equations}
    \end{center}
\end{table*}

@@

Internal to \pysr, a multi-objective optimization problem is solved: the evolution seeks to find expressions which are as accurate as possible, while being as simple as possible.
Formally, for our setting, \pysr solves the following optimization problem:
\begin{align}
    s_c &= 
        \mathop{\arg\min}_{
            \tiny
            \begin{array}{c}s\in\mathcal{S}\\ \abs{s} = c \end{array}
        }
        \mathcal{L}(s),
    \quad\text{for each } c\in \mathcal{C},\nonumber\\
    &\text{where }\mathcal{L}(s) = \sum_i \ell(s(\mathbf{x}_i), y_i)
\end{align}
where $s$ is an expression, 
$\mathcal{S}$ is a space of possible expressions considered,
$\abs{s}$ is the complexity of an expression $s$,
$\ell$ is the loss function, and $\{(x_i, y_i)\}$ is the dataset
for $x_i$ each input and $y_i$ the label.
The most accurate expression at each $c$, denoted as $s_c$, is computed for a given set range of $c$, which we choose as $c\in\mathcal{C}\equiv \{1, \ldots, 50\}$.
Complexity is defined here
as the number of symbols in the expression (including repeats),
and $\ell$ is defined as $(\hat{y}_i, y_i) = \qty(\hat{y}_i - y_i)^2$.

>>>>

\begin{table*}[hbt!]
    \begin{center}
    \begin{tabular}{ l l l l }
    \hline
    \hline
    Complexity &  Score & Loss & Expression for $\text{Rate}[\text{yr}^{-1}](M=M/M_\odot)$\\
    \hline
    \hline
    16 & 0.126   & 0.212  & $3.72 \rm{Cond}{\left(M - 9.27,0.9^{M} \right)} + 3.72 \rm{Gauss}{\left(0.52 M - 4.85 \right)}$\\[0.4em]
    % Add more space between rows of table^
    25 & 0.501   & 0.0352 & $3.89 \left(\rm{Gauss}{\left(0.19 M - 6.54 \right)} + 0.45\right) \rm{Cond}{\left(M - 9.12,0.91^{M} \right)}$\\
    & & & $ + 3.89 \rm{Gauss}{\left(0.5 M - 4.8 \right)}$\\[0.4em]
    48 & 0.00771 & 0.0108 & $\left(\rm{Cond}{\left(M - 9.42,0.62 \cdot 0.9^{M} \right)} + 1.44 \rm{Gauss}{\left(0.51 M - 4.88 \right)}\right)$\\
    & & & $\left(5.11 \rm{Gauss}{\left(0.06 M - 4.67 \right)} + 7.82 \rm{Gauss}{\left(0.17 M - 5.86 \right)} + 3.26\right)$\\
    \hline
    \hline
    \end{tabular}
    \caption{Expressions obtained through symbolic regression with \pysr.
    In the search we perform, there are 30 equations with different complexities.
    We select three representative equations from the Pareto front by setting three successive complexity ranges, and selecting the highest scoring expression in each range.}
    \label{tab:equations}
    \end{center}
\end{table*}

@@

Internal to \pysr, a multi-objective optimization problem is solved: the evolution seeks to find expressions which are as accurate as possible, while being as simple as possible.
Formally, for our setting, \pysr solves the following optimization problem:
\begin{align}
    s_c &= 
        \mathop{\arg\min}_{
            \tiny
            \begin{array}{c}s\in\mathcal{S}\\ \abs{s} = c \end{array}
        }
        \mathcal{L}(s),
    \quad\text{for each } c\in \mathcal{C},\nonumber
\end{align}
where the loss function $\mathcal{L}$ is defined as:
\begin{equation}
\mathcal{L}(s) = \sum_i \ell(s(\mathbf{x}_i), y_i),
\end{equation}
where $s$ is an expression, 
$\mathcal{S}$ is a space of possible expressions considered,
$\abs{s}$ is the complexity of an expression $s$,
$\ell$ is the loss function, and $\{(x_i, y_i)\}$ is the dataset
for $x_i$ each input and $y_i$ the label.
The most accurate expression at each $c$, denoted as $s_c$, is computed for a given set range of $c$, which we choose as $c\in\mathcal{C}\equiv \{1, \ldots, 50\}$.
Complexity is defined here
as the number of symbols in the expression (including repeats),
and $\ell$ is defined as $(\hat{y}_i, y_i) = \qty(\hat{y}_i - y_i)^2$.
